---
title: "R Markdown Presentation & Plotly"
author: "Loo Yik Herr"
date: "9/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Instructions
Create a web page presentation using R Markdown that features a plot created with Plotly. 
Host your webpage on either GitHub Pages, RPubs, or NeoCities. 
Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 
We would love to see you show off your creativity!

## Review criteria
The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Assignment
Here is the India Gate, Qutb Minar, Red Fort, Humayun’s Tomb, Gurudwara Bangla Sahib, Akshardham some of the Visiting locations in Delhi, Capital of India

```{r}
library(plotly)
```
### 3D Surface Plot
```{r}
plot_ly(z=volcano, type="surface")
```

### Boxplot

When you zoom in to each cluster, the cluster will seperate until you see the individual Markers!!

```{r}
p <- plot_ly(midwest, x = ~percollege, color = ~state, type = "box")
p  

